|

### 2022-11-09 manuscript.Rmd
add page number

Some people may wonder why we need to teach accessibility as part of an introductory data science course as opposed to covering accessibility in a separate and general course module. According to the recent faculty survey on teaching accessibility [@shinoharaWhoTeachesAccessibility2018], the most critical barriers to teaching accessibility reported by 1,857 faculty from 318 institutions were "the absence of clear and *discipline-specific accessibility* [emphasis added] learning objectives and the lack of faculty knowledge about accessibility." <!-- Need to find the exact page number for this quote -->
This reveals faculty often have trouble making sense of how they can integrate accessibility into their specific teaching domains, which requires applied knowledge of accessibility beyond general concepts.

>>>>

Some people may wonder why we need to teach accessibility as part of an introductory data science course as opposed to covering accessibility in a separate and general course module. According to the recent faculty survey on teaching accessibility [@shinoharaWhoTeachesAccessibility2018], the most critical barriers to teaching accessibility reported by 1,857 faculty from 318 institutions were "the absence of clear and *discipline-specific accessibility* [emphasis added] learning objectives and the lack of faculty knowledge about accessibility" (p. 197).
This reveals faculty often have trouble making sense of how they can integrate accessibility into their specific teaching domains, which requires applied knowledge of accessibility beyond general concepts.
